IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-10-16 paper/real.tex
remove Haskell and C explanations

\subsection{Haskell}
\label{sec:real:hs}
Our work borrows ideas from a Haskell coarse-grained IFC
system called LIO~\cite{lio, stefan:addressing-covert}.
%
LIO relies on Haskell's strong type system and monadic encoding of
side-effecting computations to achieve isolation and define the IFC
sub-language.
%
Specifically LIO provides the \verb|LIO| monad as a way of restricting
(almost all) side-effects; this monad also keeps track of a current
label which is, in turn, used by trusted code when defining core IFC
functions, such as |getLabel|.
%
In the context of our framework, LIO can be understood as follows: the
\emph{pure subset} of Haskell is the target language, while the
monadic subset of Haskell, operating in the \verb|LIO| monad, is the
IFC language.

%Indeed, by rephrasing LIO in terms of our framework, we simplified
%LIO's treatment of exceptions.
%
LIO originally associated labels with exceptions, in a
similar style to fine-grained
systems~\cite{stefan:2012:arxiv-flexible, Hritcu:2013:YIB:2497621.2498098}.
%
In particular, the label of an exception was set to the current label
at the time of the throw, and used by a custom catch construct to
raise the current label, thereby preventing leaks due to exceptional
control flows.
%
In addition to being overly complex, the interaction of exceptions
with clearance (which sets an upper bound on the current label, see
Section~\ref{sec:clearance}) was incorrect: the clearance
was restored to the clearance at point of the catch (a consequence of
defining \verb|LIO| using a State monad).
%
Furthermore, pure exceptions (e.g., divide by zero) always percolated to
trusted code, effectively allowing for denial of service attacks.
%
The insights gained when viewing coarse-grained IFC as presented in this
paper led to a much cleaner, simpler treatment of exceptions in LIO,
which has now been adapted by LIO.
%By using isolated tasks, and thus treating the current label (and
%clearance) as global, the underlying Haskell exception system can be
%used directly: exceptional control flow does not affect IFC.

\subsection{C}
\label{sec:real:c}
%
C programs are able to execute arbitrary (machine) code, access
arbitrary memory, and perform arbitrary system calls.
%
Thus, the confinement of C programs must be imposed by the underlying OS
and hardware.
%
For instance, our notion of isolation can be achieved using Dune's
hardware protection mechanisms~\cite{Belay:2012:DSU:2387880.2387913},
similar to a simpler version of
Wedge~\cite{Belay:2012:DSU:2387880.2387913,
Bittau:2008:WSA:1387589.1387611} with an information flow control
policy.
%
Using page tables, a (trusted) IFC runtime could ensure that each task,
implemented as a lightweight process, can only access the memory it
allocates---tasks do not have access to any shared memory.
%
In addition, ring protection could be used to intercept system
calls performed by
a task and only permit those corresponding to our IFC language (such as
|getLabel| or |send|).
%
Dune's hardware protection mechanism would allow us to provide a concrete
implementation that is efficient and relatively simple to reason
about, but other sandboxing mechanisms could be used in place of Dune.

In this setting, the combined language of Section~\ref{sec:retrofit}
can be interpreted in the following way: calling from the target
language to the IFC language corresponds to invoking a system call.
%
Creating a new task with the |sandbox| system call corresponds to
\emph{forking} a process.  Using page tables we can ensure that
there will be no shared memory
(effectively
defining |ap klone tS
= tS0|, where |tS0| is the set of pages necessary to bootstrap a
lightweight process.)
%
Similarly, control over page tables and protection bits allows us to
define a |send| syscall that copies pages to our
(trusted) runtime queue; and, correspondingly, a |recv| that copies
the pages from the runtime queue to the (untrusted) receiver.
%
Since C is not memory safe, conditions on these system calls are
meaningless.
%
We leave the implementation of this IFC system for C to future work.

>>>>

%% \subsection{Haskell}
%% \label{sec:real:hs}
%% Our work borrows ideas from a Haskell coarse-grained IFC
%% system called LIO~\cite{lio, stefan:addressing-covert}.
%% %
%% LIO relies on Haskell's strong type system and monadic encoding of
%% side-effecting computations to achieve isolation and define the IFC
%% sub-language.
%% %
%% Specifically LIO provides the \verb|LIO| monad as a way of restricting
%% (almost all) side-effects; this monad also keeps track of a current
%% label which is, in turn, used by trusted code when defining core IFC
%% functions, such as |getLabel|.
%% %
%% In the context of our framework, LIO can be understood as follows: the
%% \emph{pure subset} of Haskell is the target language, while the
%% monadic subset of Haskell, operating in the \verb|LIO| monad, is the
%% IFC language.

%% %Indeed, by rephrasing LIO in terms of our framework, we simplified
%% %LIO's treatment of exceptions.
%% %
%% LIO originally associated labels with exceptions, in a
%% similar style to fine-grained
%% systems~\cite{stefan:2012:arxiv-flexible, Hritcu:2013:YIB:2497621.2498098}.
%% %
%% In particular, the label of an exception was set to the current label
%% at the time of the throw, and used by a custom catch construct to
%% raise the current label, thereby preventing leaks due to exceptional
%% control flows.
%% %
%% In addition to being overly complex, the interaction of exceptions
%% with clearance (which sets an upper bound on the current label, see
%% Section~\ref{sec:clearance}) was incorrect: the clearance
%% was restored to the clearance at point of the catch (a consequence of
%% defining \verb|LIO| using a State monad).
%% %
%% Furthermore, pure exceptions (e.g., divide by zero) always percolated to
%% trusted code, effectively allowing for denial of service attacks.
%% %
%% The insights gained when viewing coarse-grained IFC as presented in this
%% paper led to a much cleaner, simpler treatment of exceptions in LIO,
%% which has now been adapted by LIO.
%% %By using isolated tasks, and thus treating the current label (and
%% %clearance) as global, the underlying Haskell exception system can be
%% %used directly: exceptional control flow does not affect IFC.

%% \subsection{C}
%% \label{sec:real:c}
%% %
%% C programs are able to execute arbitrary (machine) code, access
%% arbitrary memory, and perform arbitrary system calls.
%% %
%% Thus, the confinement of C programs must be imposed by the underlying OS
%% and hardware.
%% %
%% For instance, our notion of isolation can be achieved using Dune's
%% hardware protection mechanisms~\cite{Belay:2012:DSU:2387880.2387913},
%% similar to a simpler version of
%% Wedge~\cite{Belay:2012:DSU:2387880.2387913,
%% Bittau:2008:WSA:1387589.1387611} with an information flow control
%% policy.
%% %
%% Using page tables, a (trusted) IFC runtime could ensure that each task,
%% implemented as a lightweight process, can only access the memory it
%% allocates---tasks do not have access to any shared memory.
%% %
%% In addition, ring protection could be used to intercept system
%% calls performed by
%% a task and only permit those corresponding to our IFC language (such as
%% |getLabel| or |send|).
%% %
%% Dune's hardware protection mechanism would allow us to provide a concrete
%% implementation that is efficient and relatively simple to reason
%% about, but other sandboxing mechanisms could be used in place of Dune.

%% In this setting, the combined language of Section~\ref{sec:retrofit}
%% can be interpreted in the following way: calling from the target
%% language to the IFC language corresponds to invoking a system call.
%% %
%% Creating a new task with the |sandbox| system call corresponds to
%% \emph{forking} a process.  Using page tables we can ensure that
%% there will be no shared memory
%% (effectively
%% defining |ap klone tS
%% = tS0|, where |tS0| is the set of pages necessary to bootstrap a
%% lightweight process.)
%% %
%% Similarly, control over page tables and protection bits allows us to
%% define a |send| syscall that copies pages to our
%% (trusted) runtime queue; and, correspondingly, a |recv| that copies
%% the pages from the runtime queue to the (untrusted) receiver.
%% %
%% Since C is not memory safe, conditions on these system calls are
%% meaningless.
%% %
%% We leave the implementation of this IFC system for C to future work.
